\sysfull

### 2018-08-03 paper/asplos19/systemdescription.tex
partial commit

\textbf{Programming and Execution Model.}  To use \sys, a programmer must convert a plain C code into tasks by  designates a top-level set of functions as tasks, sequences the control-flow between these tasks, and annotates memory accesses that manipulate global data.
% In other words, it requires reasoning similar to prior task-based systems~\cite{chain,alpaca}.

>>>>

\textbf{Programming and Execution Model.}  To use \sys, a programmer must convert a plain C code into tasks by  encapsulating the conde in set of top-level set of functions (tasks), sequences the control-flow between these tasks, and annotates memory accesses that manipulate global data.
% In other words, it requires reasoning similar to prior task-based systems~\cite{chain,alpaca}.
